---
layout: page
title: Antigen processing on Google Scholar
output: html_document
---

This ended up being is as much about what scraping data from Google Scholar 
can't do, as what it can. However, hopefully it is not completely uninformative
and provides a way into the literature for uninitiated.

### Summary
What follows was inspired by a blog post by Jeff Leek from 
[Simply Statistics](http://simplystatistics.org/2015/01/16/if-you-were-going-to-write-a-paper-about-the-false-discovery-rate-you-should-have-done-it-in-2002/).
I've hacked his code to my own ends here, and you can find all the code for
and raw data for doing something similar on my [GitHub repo](https://github.com/ab604/ap-stats).

The aim was to get a sense of what has happened/is happening in the field of
MHC class I antigen processing by scraping the top hits from Google Scholar for
a collection of antigen processing related terms.
[About Google Scholar](http://scholar.google.co.uk/intl/en/scholar/about.html)
suggests Google Scholar is driven largely by citations.

By examining when the most cited papers were published it provides a sense of
when the key discoveries were made, and which topics are hot or cold. (Which 
might be handy for choosing future work).

**However** I also discovered that Google is very sensitive to the search terms and 
whilst scraping the most cited papers is easy, they aren't necessarily the most
relevant, especially where MHC I is concerned.

If you are familiar with the field, the results may seem intuitive. Indeed you
may be able to map your own career to the timings of the publications. Or you 
may just be infuriated that I didn't find the papers you consider the most 
important. :-)

Below you can see what I did and what I found in the form of box-plots and some
interactive tables.

### Search terms used
Initially I searched on 8 search terms for the **key players** in the MHC I 
antigen processing pathway. These terms were:
```{r,echo=FALSE,comment=""}
load("../cache/ap.terms.RData")
print(ap.terms,quote=FALSE)
```

And then I did a second round for **MHC I specific** search terms to split MHC I 
papers into categories using the original search term, and then for paper to do 
with structure, conformation change and peptide repertoire. These terms were:
```{r,echo=FALSE,comment=""}
load("../cache/mhc.terms.RData")
print(mhc.terms,quote=FALSE)
```

### Boxplots of the search results
Having performed the searches I've plotted the results as box-plots for the key
players:

```{r, echo=FALSE}
library(ggplot2)
load("../cache/plot.ap.RData")
# Create plot
p1 <- ggplot(plot.ap,aes(x=ap.term_vec,y=ap.pubyear_vec)) +
        # Apply aesthetics
        geom_boxplot() +
        xlab("") +
        # Amend y-axis label
        ylab("Publication Year") +
        # Create yearly ticks 
        scale_y_continuous(breaks=seq(1980,2015,5)) +
        # Remove the legend title
        #theme(legend.title=element_blank()) +
        # Add a plot title
        ggtitle("Publication Year of First 30 Google Scholar Hits")

print(p1)
```

The median publication date for each category is:

```{r,echo=FALSE,comment=""}
load("../cache/ap.median.RData")
print(ap.median)
```

And here's box-plot for the MHC I categories MHC I molecule, MHC I structure, 
MHC I conformational change and MHC I peptide repertoire:

```{r, echo=FALSE}
library(ggplot2)
load("../cache/plot.mhc.RData")
plot.title <- bquote(atop('Publication Year of First 30 Google Scholar Hits' , 
                          'for MHC I related search terms'))

# Create plot
p2 <- ggplot(plot.mhc,aes(x=mhc.term_vec,y=mhc.pubyear_vec)) +
        # Apply aesthetics
        geom_boxplot() +
        xlab("") +
        # Amend y-axis label
        ylab("Publication Year") +
        # Create yearly ticks 
        scale_y_continuous(breaks=seq(1980,2015,5)) +
        # Remove the legend title
        #theme(legend.title=element_blank()) +
        # Add a plot title
        ggtitle(plot.title)

print(p2)
```

With the median publication dates for these categories:


```{r,echo=FALSE,comment=""}
load("../cache/mhc.median.RData")
print(mhc.median)
```

### Tables of the papers scraped for each search

####ERAP1

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/eraptab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

####Tapasin

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/tpntab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

####MHC I molecule

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/moltab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

####Calreticulin

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/cartab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

####Erp57

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/erptab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

####Calnexin

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/clntab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

####TAPBPR

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/tprtab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

####UGGT

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/ugtab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

####MHC I structure

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/sructab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

####MHC I conformational change

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/conftab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```

###MHC I peptide reportoire

```{r,echo=FALSE}
library(DT)
erapt <- read.table("../src/peptab.txt")
datatable(erapt, colnames = c('First Author', 'Paper Title', 'Publication Year', 'No. of Citations'))
```
